### 2020-07-16 msr.tex
minor edit

The reference start-up salt composition for the fuel and blanket salts is
77.5\% LiF - 22.5\% AcF$_4$ (actinide fluorides)
\cite{merle-lucotte_launching_2011}. Some researchers working with the
\gls{MSFR} model tweak the exact actinide composition by varying the
$^{232}$Th to $^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a
uniform temperature of 973 K \cite{brovchenko_neutronic_2019} or for other
motivations \cite{fiorina_molten_2013} \cite{pettersen_coupled_2016}. Thus,
the exact actinide compositions vary depending on the nuclear data library,
neutron transport code, and the purpose of the study. The present work uses
a fuel salt composition of 77.5\% LiF - 19.913\% ThF$_4$ - 2.587\%
$^{233}$UF$_4$ for all calculations, which gives steady-state inlet and outlet
temperatures approximately equal to the nominal values in Table
\ref{table:msfr}. Table \ref{table:prip} shows relevant physical properties of
the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$
\cite{brovchenko_neutronic_2019}.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $0.01015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $1.010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1594$ & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}

>>>>

The reference start-up salt composition for the fuel and blanket salts is
77.5\% LiF - 22.5\% AcF$_4$ (actinide fluorides)
\cite{merle-lucotte_launching_2011}. Some researchers working with the
\gls{MSFR} model tweak the exact actinide composition by varying the
$^{232}$Th to $^{233}$U ratio to obtain a $k_{\text{eff}}$ value of 1 at a
uniform temperature of 973 K \cite{brovchenko_neutronic_2019} or for other
purposes \cite{fiorina_molten_2013, pettersen_coupled_2016}. Thus,
the exact actinide compositions vary depending on the nuclear data library,
neutron transport code, and the purpose of the study. The present work uses
a fuel salt composition of 77.5\% LiF - 19.913\% ThF$_4$ - 2.587\%
$^{233}$UF$_4$ for all calculations, which gives steady-state inlet and outlet
temperatures approximately equal to the nominal values in Table
\ref{table:msfr}. Table \ref{table:prip} shows relevant physical properties of
the fuel and blanket salts.
%
\begin{table}[htb!]
\small
\centering
\caption{Properties of the fuel and blanket salts LiF-AcF$_4$
\cite{brovchenko_neutronic_2019}.}
\begin{tabular}{l l r r}
\toprule
Property & Formula & {Value at 973 K} & Validity Range\\
\midrule
Melting temperature [K] & 841 & {N/A} & 1 bar \\
Density, $\rho$ [kg m$^{-3}$] & $4094-0.882 \cdot (T-1008)$ & $4125$ & 893-1123 K \\
Dynamic viscosity, $\mu$ [Pa s] & $\rho \cdot 5.55 \times 10^{-8} \cdot e^{3689/T}$ & $0.01015$ & 898-1121 K \\
Thermal conductivity, $k$ [W m$^{-1}$ K$^{-1}$] & $0.928+8.397 \times 10^{-5} \cdot T$ & $1.010$ & 891-1020 K \\
Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111+2.78\cdot T$ & $1594$ & 867-907 K \\
\bottomrule
\end{tabular}
\label{table:prip}
\end{table}
